---
title: "cytoEx: Exhaustive autogating for openCyto"
author: "Mike Jiang"
date: "September 27, 2016"
output: 
  html_document: 
    keep_md: yes
---

This package fully automates the `openCyto` gating without the need of prior knowledge about the gating hierarhcy.
It creates the gating tree automatically by selecting the best marker/parameter at each level.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```
```{r }
library(openCyto)
library(cytoEx)
```

## Load existing gating set
```{r}

dataDir <- system.file("extdata",package="flowWorkspaceData")
gs <- load_gs(list.files(dataDir, pattern = "gs_manual",full = TRUE))
```

## create a copy of gs
```{r}
gs2 <- clone(gs, isNew = FALSE, isEmpty = FALSE)
```

## Start from singlets node
```{r}
for(node in getChildren(gs2, "singlets"))
  Rm(node, gs2)
```

## Run the exhaustive gating using `openCyto::mindensity`
```{r}
gating("singlets", gs2, gating.function = mindensity)
```

## plot the results
```{r}
plot(gs2)
library(ggcyto)
autoplot(gs2[[1]])
```

## Inspect the gating tree interactively by shinyCyto
```{r treeGadget, eval=FALSE}
shinyCyto::gatingTreeApp(gs2)
```

